Experimental plan

### 2013-09-30 report/experiments.tex
Added notes for 1d spring experiments
Added experiments plan and modified spring system

\title{}
\author{Malte Stær Nissen}

@@

Til triangulering:
qmesh,
delaunay,

Store trekanter med små trekanter i midten.

Fast forhold mellem tidsskridt til at starte med.

Derefter detekt når advektionen går galt.

$\frac{\alpha t}{2} < \Delta t$

linære beregninger

Samtidig timestepping uden genberegning på store skridt

Forsøg at se hvor meget vi kan presse citronen.

Benyt eget lille framework og modificer det

Evt. benyt lokale timesteps med genberegninger løbende

>>>>

\title{Experimental plan}
\author{Malte Stær Nissen}

@@

The experimental plan is overall split in two parts: 1 dimensional experiments and 2
dimensional experiments.

\subsection{1 dimensional experiments}
We are working with the problem of simulating a spring mass particle system in 1
dimension. Our hypothesis is that we are able to apply adaptive timestepping to
the simulation and thereby decrease the number of computations needed to
simulate the system.

We first experiment with a uniform 1D mesh where we manually choose different
timestep sizes to test for possible side-effects in as simple a simulation as
possible.

We then perform the adaptive timestepping on a 1D mesh having coarse and finer
parts.

\subsection{2 dimensional experiments}

In 2 dimensions we are working with the problem of simulating hyperelastic
materials using adaptive timestepping as for the 1 dimensional experiments.

We split the 2D experiments in a test on a somewhat uniform 2D mesh having
manually chosen some triangles to be simumlated with smaller timesteps than
others. After these experiments we move on to performing 2D experiments on
space-adaptive meshes having both coarse and fine parts.

\subsection{Comparative experiments}

Finally we are going to compare the performance of the adaptive timestepping
with regular timestepping schemes in 2 dimensions.

%Lav 1 dimensionelle problemer først med fjedrer
%
%Til triangulering:
%qmesh,
%delaunay,
%
%Store trekanter med små trekanter i midten.
%
%Fast forhold mellem tidsskridt til at starte med.
%
%Derefter detekt når advektionen går galt.
%Når arealet er lig 0
%Krydsprodukt til udregningerne.
%
%$\frac{\alpha t}{2} < \Delta t$
%
%linære beregninger
%
%Samtidig timestepping uden genberegning på store skridt
%
%Forsøg at se hvor meget vi kan presse citronen.
%
%Benyt eget lille framework og modificer det
%
%
%Evt. benyt lokale timesteps med genberegninger løbende
